Identifying regime transitions for water governance at the Yellow River Basin, China

### 2023-10-10 paper/diff/manuscript_v-8.3.0.tex
docs(paper): :memo: response letter finished
give Shuai Wang for some feedback

\documentclass[draft]{../agujournal2019}
\usepackage{url} \usepackage{lineno}
\usepackage[inline]{../trackchanges} \usepackage{soul}
\usepackage{amsmath}
\usepackage{pifont}  \linenumbers

@@

Environmental context, social atmosphere, and policies played roles in all three periods.
We calculated the ratios of regional and basinal water use for each reservoir (R/B ratio) (Figure~\ref{fig:Causes}C), with a higher ratio representing a potential role in water supply rather than basinal regulations.
Under the banner of ``conquering nature'' most of the reservoirs were built in regions with high water demands during the P1 (R/B ratios were significantly higher ($p<0.01$, see Figure~\ref{fig:Causes}C)).
Ensuing the P2, the number of new reservoirs decreased but boosted their role in water regulating and management (more red circles in Figure~\ref{fig:Causes}~C, and larger water conveyance variability in Supporting Informations Figure~S7).  Basin policies significantly increased, rigorously controlled the allocation of water (Figure~\ref{fig:Causes}D, $p<0.01$).
During the P3, authorities proposed more national-level water governance policies under the guidance of the national strategy ``environmental regulation'' (Figure~\ref{fig:Causes}D).
The regime shift from P1 to P2 is in line with the increasing water supply and demands; while driven by regulatory policies and efficiency enhancement under stable water stress from P2 to P3.

@@

In the case of the YRB, our results show that there have been three distinct governance regimes; we named them: a massive supply regime (P1: $1965 \sim 1978$), a governance transforming regime (P2: $1979 \sim 2001$), and an adaptation oriented regime (P3: $2002 \sim 2013$) (Figure~\ref{fig:IWGI}).
During the massive supply regime with lower water stress ($1965 \sim 1978$ in the YRB), water governance thus tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels (Figure~\ref{fig:Causes}~B).
As the Chinese slogan ``human will conquer nature'' suggested then, however, the enhancement of water supply did not align with irreversible changes in the human-water relationship; it drastically increased water demand with little consideration for ecological conservation~\cite{zhou2020}.
The rapid expansion of irrigated farmland and water diversion facilities in the same decade brought the overburdened YRB close to a critical point (Figure~\ref{fig:Causes}), where increasing supply to meet demand was impractical~\cite{loch2020}.
Use of over $80\%$ of the surface water since 1972 has led to frequent river depletion, causing additional ecological issues such as wetland shrinkage and declines in biodiversity~\cite{wang2019c}.
In addition, since water stress also limited the growing industrial economy, the existing modes of water governance led to a social-ecological crisis~\cite{wohlfart2016}.

The start of the governance transforming regime (P2: $1979 \sim 2001$) coincided with rising competition for water use after the ``reform and opening-up'' (Figure~\ref{fig:Causes}~C).
The results from the YRB mirror those of the theoretical analysis: continuous increases in water demand when the basin's total supply is stable can follow substantial changes in governance regime and a rapid enhancement in overall social adaptive capacity~\cite{loch2020}.
As a pioneer in shifting governing institutions, the YRB triggered institutional changes during this regime. These include, for example, slowing the growth of irrigated acreage and leading water-saving infrastructure (Figure~\ref{fig:Causes}); creation of China's first water quota scheme, and the creation of a preliminary cross-boundary water transfer plan~\cite{wang2019e,long2020,nickum2021}.
Consequently, although water stress remained and increased (due to reducing streamflow and flexibility), the last depletion of the Yellow River in 1999 led to a climax in this transformation in water governance~\cite{wang2019e}.

@@

In general, water governance of the YRB is among the most prominent example in the widespread transition to a hydrosocial cycle -``improving supply, transforming governance, and enhancing adaptation''.
To support water use in early stage (Figure~\ref{fig:summary}~A), strategies tend to manage natural water processes in order to maintain the provisioning (larger) and non-provisioning water (less).
At the later stage (Figure~\ref{fig:summary}~B), emphasis is governing across the whole basin, water governance practices are adaptively designed to meet the increasing needs of the socio-economic system and carried out.
With the above gradually shifting, the emergence of different regimes drives water governance challenges at a basin-scale: these were primarily economic and environmental before the transformation, but social and policy-related towards the end (Figure~\ref{fig:summary})~\cite{singh2019,porcher2019}.
In an analogy at a global scale, the resource challenges, represented by water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins~\cite{allan2019,speed2013,liu2012}.
Highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures~\cite{unep-dhi2016,mirumachi2015}.
Linking regime shifts to the governance challenges, the implementation of IWGI thus offers a comprehensive and straightforward way to interpret the intertwines between water governance and the hydrosocial transition.

>>>>

\documentclass[draft]{../agujournal2019}
\usepackage{url} \usepackage{lineno}
\usepackage[inline]{../trackchanges} \usepackage{soul}
\usepackage{amsmath}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{pifont}  \linenumbers

@@

Environmental and social contexts, governance policies played roles in all three periods.
We calculated the ratios of regional and basinal water use for each reservoir (R/B ratio) (Figure~\ref{fig:Causes}C), with a higher ratio representing a potential role in water supply rather than basinal regulations.
Under the banner of ``conquering nature'' most of the reservoirs were built in regions with high water demands during the P1 (R/B ratios were significantly higher ($p<0.01$, see Figure~\ref{fig:Causes}C)).
Ensuing the P2, the number of new reservoirs decreased but boosted their role in water regulating and management (more red circles in Figure~\ref{fig:Causes}~C, and larger water conveyance variability in Supporting Informations Figure~S8).
Basin policies significantly increased, rigorously controlled the allocation of water (Figure~\ref{fig:Causes}D, $p<0.01$).
During the P3, authorities proposed more national-level water governance policies under the guidance of the national strategy ``environmental regulation'' (Figure~\ref{fig:Causes}D).
The regime shift from P1 to P2 is in line with the increasing water supply and demands; while driven by regulatory policies and efficiency enhancement under stable water stress from P2 to P3.

@@

In the case of the YRB, our results show that there have been three distinct governance regimes; we named them: a massive supply regime (P1: $1965 \sim 1978$), a governance transforming regime (P2: $1979 \sim 2001$), and an adaptation oriented regime (P3: $2002 \sim 2013$) (Figure~\ref{fig:IWGI} and Table~\ref{tab:regimes}).
These regime shifts, as comprehensive outcomes of complex human-water interactions, are coincidentally well presented by several well-known and dominated social atmospheres in China (Table~\ref{tab:regimes}).
The social atmospheres refers to the sociocultural context in which people live or in which something happens, underlying the direction of practices of water governance during a regime, despite lack of strict causality evidence.

During the massive supply regime ($1965 \sim 1978$ in the YRB), water governance tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels (Figure~\ref{fig:Causes}~B).
As the Chinese slogan ``human will conquer nature'' suggested then, however, the enhancement of water supply did not align with irreversible changes in the human-water relationship; it drastically increased water demand with little consideration for ecological conservation~\cite{zhou2020}.
The rapid expansion of irrigated farmland and water diversion facilities in the same decade brought the overburdened YRB close to a critical point (Figure~\ref{fig:Causes}), where increasing supply to meet demand was impractical~\cite{loch2020}.
Use of over $80\%$ of the surface water since 1972 has led to frequent river depletion, causing additional ecological issues such as wetland shrinkage and declines in biodiversity~\cite{wang2019c}.
In addition, since water stress also limited the growing industrial economy, the existing modes of water governance led to a social-ecological crisis~\cite{wohlfart2016}.

\begin{table}[htbp]
    \centering
    \caption{Brief summary of regime transitions for water governance at the Yellow River Basin}
      \begin{tabularx}{\textwidth}{p{0.15\textwidth} p{0.15\textwidth} p{0.2\textwidth} p{0.5\textwidth}}
      \toprule
      Time  & Closet social atmosphere$^*$ & Regime & Main trait \\
      \midrule
      $1965-1978$ & 1960s: Conquering nature & massive supply regime & boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels \\
      $1979-2001$ & 1978: reform and opening-up & governance transforming regime & triggered institutional changes for rapid enhancement of overall social adaptive capacity to severe water stresses \\
      $2002-2013$ & 2002: Environmental regulating & adaptation-oriented regime & adapting to stable high water stress with trade-offs between water-dependent regions and sectors \\
      \bottomrule
      \end{tabularx}\label{tab:regimes}

      \footnotesize
      $^*$ Social atmosphere refers to the sociocultural context in which people live or in which something happens, including the culture that the individual was educated or lives.
  \end{table}
The start of the governance transforming regime (P2: $1979 \sim 2001$) coincided with rising competition for water use after the ``reform and opening-up'' (Figure~\ref{fig:Causes}~C).
The results from the YRB mirror those of the theoretical analysis: continuous increases in water demand when the basin's total supply is stable can follow substantial changes in governance regime and a rapid enhancement in overall social adaptive capacity~\cite{loch2020}.
As a pioneer in shifting governing institutions, the YRB triggered institutional changes during this regime. These include, for example, slowing the growth of irrigated acreage and leading water-saving infrastructure (Figure~\ref{fig:Causes}); creation of China's first water quota scheme, and the creation of a preliminary cross-boundary water transfer plan~\cite{wang2019e,long2020,nickum2021}.
Consequently, although water stress remained and increased (due to reducing streamflow and flexibility), the last depletion of the Yellow River in 1999 led to a climax in this transformation in water governance~\cite{wang2019e}.

@@

In general, water governance of the YRB is among the most prominent example in the widespread transition to a hydrosocial cycle -``improving supply, transforming governance, and enhancing adaptation''.
To support water use in early stage (Figure~\ref{fig:summary}~A), strategies tend to manage natural water cycle in order to maintain the provisioning (larger) and non-provisioning water (less).
At the later stage (Figure~\ref{fig:summary}~B), emphasis is governing across the whole basin, water governance practices are adaptively designed to meet the increasing needs of the socio-economic system and carried out.
With the above gradually shifting, the emergence of different regimes drives water governance challenges at a basin-scale: these were primarily economic and environmental before the transformation, but social and policy-related towards the end (Figure~\ref{fig:summary})~\cite{singh2019,porcher2019}.
The Yellow River basin's challenges as an example, represented by the shift in national narratives from conquering nature for economy and eliminating pollution to stressing of harmonious human-water, increased the importance of administrative measures in resolving water-related disputes.
It demonstrates again that highly-controlled and developed basins (especially for transboundary rivers) must resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures~\cite{unep-dhi2016,mirumachi2015}.
Linking regime shifts to the governance challenges, the implementation of IWGI thus offers a comprehensive and straightforward way to interpret the intertwines between water governance and the hydrosocial transition.

### 2023-10-10 paper/letter/cover_letter_r2.tex
docs(paper): :memo: response letter finished
give Shuai Wang for some feedback

Thank you for the opportunity to revise our manuscript titled ``Identifying regime transitions for water governance at a basin scale'' We appreciate the constructive feedback provided by the reviewers and believe that our revised manuscript more effectively addresses their concerns.

% 很抱歉我们花了这么长时间来返修，但正如您看到的，我们在新的版本中补充了很多内容和图表，努力回应审稿人和编辑的一切关切。我们也花时间试着联系了数据的作者团队。在得知正文中数据短时间内无法增补到最新年份后，我们使用其它数据源再次计算了IWGI，从而努力增强结果的鲁棒性。
I'm sorry it took us so long to go back, but as you can see, we've added a lot of content and graphics to the new version in an effort to respond to all the concerns of reviewers and editors. We also took the time to try to contact the team that authored the data. After learning that the data in the text could not be updated to the latest year for a short time, we supplement analysis using other data sources in an effort to enhance the robustness of the results.
In response to the reviewers' feedback, we also restructured the introduction and discussion sections to provide a more supportive and solid content of the results.

We believe that these revisions have significantly improved the quality and value of our manuscript, and we hope that you will find it suitable for publication in Water Resources Research. We are confident that our study makes a valuable contribution to the understanding of water governance in China and beyond.

The revised manuscript includes the main body of text with $4423$ words and $4$ figures; the supporting information with $4$ sections has $9$ supporting figures and $1$ supporting tables. Furthermore, we declare no conflicts of interest to disclose.

>>>>

% 我们写信是为了提交我们的手稿的修订版，题为“确定中国黄河流域水治理的政权过渡”，供您和审稿人考虑。我们非常感谢审稿人提供的建设性意见，这些意见有助于提高我们工作的质量和清晰度。
We are writing to submit the revised version of our manuscript titled ``Identifying regime transitions for water governance at the Yellow River Basin, China'' for your and the reviewers’ consideration. We are grateful for the constructive feedback provided by the reviewers, which has been instrumental in enhancing the quality and clarity of our work.

One of the significant revisions in our manuscript involves the robustness check for the identified breakpoints in our study. Furthermore, we have addressed all the specific comments and suggestions raised by the reviewers meticulously. We introduced a new table and expanded the discussion to provide more comprehensive insights. These clarifications and modifications made in response to both reviewers’ inputs, have significantly enriched the content and narrative of our manuscript.

We believe that these revisions have addressed the reviewers’ concerns effectively and hope that the enhancements made will meet their expectations and standards of quality for publication in \textit{Water Resources Research}.

The revised manuscript includes the main body of text with $4423$ words and $4$ figures with $1$ table; the supporting information with $4$ sections has $9$ supporting figures and $2$ supporting tables. Furthermore, we declare no conflicts of interest to disclose.

### 2023-10-10 paper/response_letter/source/editor.tex
docs(paper): :memo: response letter finished
give Shuai Wang for some feedback

\subsection{Remarks to Author}
\RC{} Dear Authors, thank you for the carful revisions. Our original referees have re-evaluated the revised manuscripts. While they are satisfied with most of the revisions, they find that some of their earlier comments were not fully addressed.

@@

\AR{}

@@

>>>>

\subsection{Remarks to Author}

\RC{} Dear Authors, thank you for the carful revisions. Our original referees have re-evaluated the revised manuscripts. While they are satisfied with most of the revisions, they find that some of their earlier comments were not fully addressed.

@@

\AR{} Thanks for the suggestion. We have employed various change points detection methods, demonstrating that our results are robust and consistent. The inclusion of these additional methods underscores the validity of our initial findings and strengthens the overall credibility of our research.

@@

\AR{} Thanks for the comments. We now improved the clarity of discussion with a new table, and double-checked accessibility of the link.

### 2023-10-10 paper/response_letter/source/reviewer_1.tex
docs(paper): :memo: response letter finished
give Shuai Wang for some feedback

\begin{quote}
	% 我们同样使用一些流行的断点识别方法检验了Pettitt的断点识别结果。它们的名称、结果、参考论文可以在表中找到。所有的结果在第二个断点的识别上几乎是一致的（2000年），而第一个断点也仅有3年的差异（1975年与1978年）。
	We have also employed a series of popular change point detection methods to validate the results obtained through the Pettitt test. The names of these methods, their respective results, and the references to the pertinent literature can be found in the accompanying table~\ref{table:breakpoint-detection-methods}. A consensus was observed among all methods regarding the identification of the second change point, which consistently emerged around the year 2000. There was a minor variation of three years in the identification of the first change point, pinpointed either in 1975 or 1978.

@@

\begin{quote}
	First, for scarcity, $A_{i, j}$ is the total water use as a proportion of regional multi-year average runoff volume in year $j$ and region $i$ \dots
\end{quote}

@@

\begin{quote}
	% 以黄河流域所面临的挑战为例，国家叙事从经济征服自然、消除污染到强调人水和谐的转变，增加了行政措施在解决与水有关的纠纷中的重要性。
	The Yellow River basin's challenges as an example, represented by the shift in national narratives from conquering nature for economy and eliminating pollution to stressing of harmonious human-water, increased the importance of administrative measures in resolving water-related disputes.
\end{quote}

@@

\begin{quote}
	% 它再次表明，高度控制和开发的流域(特别是跨界河流)必须解决结构性挑战，例如水争端或缺乏公平，并且可能迫切需要新的灵活、有效的社会政治治理结构。
	It demonstrates again that highly-controlled and developed basins (especially for transboundary rivers) must resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures.
\end{quote}

>>>>

\begin{quote}[page=Supporting Informations]
	% 我们同样使用一些流行的断点识别方法检验了Pettitt的断点识别结果。它们的名称、结果、参考论文可以在表中找到。所有的结果在第二个断点的识别上几乎是一致的（2000年），而第一个断点也仅有3年的差异（1975年与1978年）。
	We have also employed a series of popular change point detection methods to validate the results obtained through the Pettitt test. The names of these methods, their respective results, and the references to the pertinent literature can be found in the accompanying table~\ref{table:breakpoint-detection-methods}. A consensus was observed among all methods regarding the identification of the second change point, which consistently emerged around the year 2000. There was a minor variation of three years in the identification of the first change point, pinpointed either in 1975 or 1978.

@@

\begin{quote}[page=5, sline=158, eline=160]
	First, for scarcity, $A_{i, j}$ is the total water use as a proportion of regional multi-year average runoff volume in year $j$ and region $i$ \dots
\end{quote}

@@

\begin{quote}[page=11, sline=320, eline=323]
	% 以黄河流域所面临的挑战为例，国家叙事从经济征服自然、消除污染到强调人水和谐的转变，增加了行政措施在解决与水有关的纠纷中的重要性。
	The Yellow River basin's challenges as an example, represented by the shift in national narratives from conquering nature for economy and eliminating pollution to stressing of harmonious human-water, increased the importance of administrative measures in resolving water-related disputes.
\end{quote}

@@

\begin{quote}[page=11, sline=323, eline=326]
	% 它再次表明，高度控制和开发的流域(特别是跨界河流)必须解决结构性挑战，例如水争端或缺乏公平，并且可能迫切需要新的灵活、有效的社会政治治理结构。
	It demonstrates again that highly-controlled and developed basins (especially for transboundary rivers) must resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures.
\end{quote}

### 2023-10-10 paper/response_letter/source/reviewer_2.tex
docs(paper): :memo: response letter finished
give Shuai Wang for some feedback

\begin{quote}
    Social atmosphere refers to the sociocultural context in which people live or in which something happens, including the culture that the individual was educated or lives.
\end{quote}

@@

\begin{quote}
    These regime shifts, as comprehensive outcomes of complex human-water interactions, are coincidentally well presented by several well-known and dominated social atmospheres (Table~1).
    The social atmospheres refers to the sociocultural context in which people live or in which something happens, underlying the direction of practices of water governance during a regime, despite lack of strict causality evidence.
\end{quote}

>>>>

\begin{quote}[page=footnotes from Figure~3 and Table~1]
    Social atmosphere refers to the sociocultural context in which people live or in which something happens, including the culture that the individual was educated or lives.
\end{quote}

@@

\begin{quote}[page=10, sline=265, eline=269]
    These regime shifts, as comprehensive outcomes of complex human-water interactions, are coincidentally well presented by several well-known and dominated social atmospheres (Table~1).
    The social atmospheres refers to the sociocultural context in which people live or in which something happens, underlying the direction of practices of water governance during a regime, despite lack of strict causality evidence.
\end{quote}
